Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-05-12 answer-to-reviewers.tex

\emph{Thanks for pointing this out, done.}

\item Frequent references to function $g$, which is only defined later in Section 5.2, make the lecture of the manuscript difficult. I suggest to rewrite the section seeking for all elements to be introduced in a more orderly fashion.

\smallskip

\emph{***Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
and to explain the details of its calculation later.
In rewriting Section~5, we now mention this more explicitely.}

@@

The weak point of the work is related to the different hypothesis which significantly simplify the modeling framework. More precisely:

\begin{enumerate}
\item All the components have the same lifetime model (namely the Weibull distribution) with a known fixed shape parameter which is not discussed. Only the scale parameter is updated and directly associated with the mean lifetime if the shape parameter is known.

\smallskip

\emph{Yes, each component type has an individual Weibull model assigned,
where the (component type specific) shape parameter is assumed to be fixed and known.
We agree that the assumption of a fixed known shape parameter is a serious limitation of our approach. 
We added a comment on this in the conclusion,
repeating a comment from the beginning of Section~4, where we wrote:
``The model could be extended to learn also the shape parameter in a later step,
using, e.g., the discretized approach by Soland (1969).''
We now also emphasize in the introduction and the conclusion that the method as described in the manuscript is deliberately kept simple
to allow for a clear and straight-forward demonstration of the general approach.
For a practical application, one should indeed update the shape parameter as well,
but in our view, adding this conceptually simple but notationally cumbersome feature would obstruct the goal of this manuscript.***}

@@

\emph{It is not possible to use data for testing the adequacy of the parametric family of the prior,
as it is supposed to reflect the expert's opinion.
So the crucial question is rather whether inverse Gamma distributions can adequately reflect the expert's opinions.
A tool to help answering that question are prior predictive distributions.
They give a distribution for the failure times that can be expected according to the expert's choice of prior
(here: inverse Gamma with specific parameters)
\textbf{in combination with the assumed sample model} (here: Weibull).
Figure~6 (previously Figure~5)*** depicts prior predictive reliability functions for the priors in the case study of Section~6,
as a way to visualize the choice of prior parameters given in Table~2 in the context of the Weibull model.
When an expert feels that these prior predictive reliability functions do not correspond to the failure time distribution (s)he postulates,
and no change of prior parameters can approximate the postulated failure time distribution,
then the prior family would seem inappropriate,
under the condition that the sample model is indeed correct.
(Methods for checking the sample model are discussed, e.g., in
Bayarri and Berger (2000), ``P values for composite null models'',
Journal of the American Statistical Association 95(452): 1127–1142.)\\
***add this reference to the paper?***}

\item Page 13, section 5.1: The grid of planned evaluation time points is defined with a ``sufficiently small’’ time increment. What does it mean quantitatively? It seems that if $\delta$ is very small the maintenance time will be almost given by $\tau_*^{(\tnow)}$.

\smallskip

\emph{We have completely rewritten Section~5 and now address the role of $\delta$ in more detail there, as well as in the Introduction.
***not sure what is meant by the second sentence.}

### 2017-05-12 cbm-rbd-paper.tex
some tweaks reacting to reviewers comments

In both cases, we decide to maintain the system preventively
when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate $\tausnow$,
since otherwise, in waiting to the next planned evaluation time,
one would exceed the optimal system failure risk 
as determined by the trade-off made via $\gnow(\cdot)$.
When $\tausnow$ is instead further in the future than the next planned evaluation time,
we can safely continue to the next planned evaluation time,
without risking to miss the cost-optimal moment to preventively maintain the system.

>>>>

In both cases, we decide to maintain the system preventively
when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate the system RLD, %$\tausnow$,
since otherwise, in waiting to the next planned evaluation time,
one would exceed the optimal system failure risk 
as determined by the trade-off made via $\gnow(\cdot)$. ***drop $\gnow(\cdot)$ here, like: ...trade-off that results in $\tausnow$.
When $\tausnow$ is instead further in the future than the next planned evaluation time,
we can safely continue to the next planned evaluation time,
without risking to miss the cost-optimal moment to preventively maintain the system.
